A Warm Sub-Neptune Transiting a Solar Twin in TESS

### 2019-10-14 paper/ms.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{periodograms.pdf}
    \caption{Lomb-Scargle periodograms of the \HARPS \RV, BIS, FWHM, and \shk timeseries measurements. Horizontal lines indicate the 5\%, 1\%, and 0.1\% false alarm probability levels. Vertical red lines mark the period of the \TESS-detected planet. The \RV, BIS, and FWHM measurements used here have been corrected for the \HARPS upgrade offset.}
    \label{fig:periodograms}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{}
    \caption{Caption}
    \label{fig:my_label}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{periodograms.pdf}
    \caption{Lomb-Scargle periodograms of the \HARPS\ \RV, BIS, FWHM, and \shk timeseries measurements. Horizontal lines indicate the 5\%, 1\%, and 0.1\% false alarm probability levels. Vertical red lines mark the period of the \TESS-detected planet. The \RV, BIS, and FWHM measurements used here have been corrected for the \HARPS upgrade offset.}
    \label{fig:periodograms}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{transits.pdf}
    \caption{De-trended lightcurve data and best-fit model for the two transit events in \TESS.}
    \label{fig:transits}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=16cm]{rvphased_1pl_wfwhm}
    \caption{Phase-folded radial velocities for \plname. Individual data points and their photon-noise-based uncertainties are shown as black points and error bars, while the grey error bars represent the uncertainties inflated by the best-fit (posterior median) jitter parameters. Green points are the error-weighted means within a series of phase bins. The best-fit model is shown as a solid orange line, with the shaded region around it marking the model's 1-$\sigma$ credible interval.}
    \label{fig:rv_phased}
\end{figure}
